---
title: "recharts_examples"
author: "scrat"
date: "2016年9月25日"
html_notebook: default
vignette: >
  %\VignetteIndexEntry{Introduce}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup} 
library(rmarkdown)
library(recharts)
library(data.table)
```

## K chart
Prepare data, volume, attr("symbol") is optional.

```{r OHLC data}
dt = data.table(datetime=as.Date("2016-01-01")+1:20,
                open = 1:20 + rnorm(20) * 5,
                close = 1:20 + rnorm(20) * 5,
                volume = runif(20) * 1000
)
dt[,high:=pmax(open,close)+runif(20)*10]
dt[,low:=pmin(open,close)-runif(20)*10]
attr(dt,"symbol") = "中国平安"
```
Plot, OHLC
```{r candlestick }
eK(dt,x=~datetime, open=~open, high=~high, low=~low, close=~close, volume = NULL)
```

Plot,  OHLC_V + markLine
```{r candlestick + volume bar} 
k2=eK(dt,x=~datetime, open=~open, high=~high, low=~low, close=~close, volume = ~volume)
k2
```

add MarkLine, color,symbol,symbolRotate,width,type are optional
```{R}
mldf1 = data.frame(x0=c("2016-01-02","2016-01-17"),y0=c(30,30), x=c("2016-01-05","2016-01-20"),y=c(20,40), color=c("steelblue","orange"), symbol="pin", symbolRotate=c(0,180), width=1,type="solid")

addMarkLine(k2, mldf1)
```


MarkPoints, color, symbol, symbolRotate are optional.
```{r}
mpdf1 = data.frame(x=c("2016-01-02","2016-01-20"),y=c(30,30), color=c("steelblue","orange"), symbol="pin", symbolRotate=c(0,180))
addMarkPoint(k2,mpdf1, series = 1)
addMarkPoint(k2,mpdf1, series = 2)
```

## Line Chart

```{r}
k3 = eLine(dt,x=~datetime, y=~high)
k3
addMarkPoint(k3, mpdf1)
```

Sugar, Chart + eXXXXX to set Options.
```{r}
k3 + eTitle(text="BLABLABLA")
```

Sugar, Chart + Vector
```{r}
k3 + rep(20,20)
```

## SCATTER Chart
Default is jitter mode. When more than 2000 points, the echart will make optimization.

```{r}
n=3000
dt2 = data.table(x=c(1:n,1:n), y=c(sin((1:n)/100),cos((1:n)/100))+rnorm(2*n,sd=0.1), label=c(rep("sin",n),rep("cos",n)))
eScatter(dt2,x=~x,y=~y,~label,symbolSize=1)
newSeriesDF = data.frame(x=1:n,y=rep(0.25,n))
addSeries(eScatter(dt2,x=~x,y=~y,series=~label,symbolSize=3),newSeriesDF)
```


## Bar Chart / HISTOGRAMS Chart

x is category, numeric. numeric breaks into category..

```{r}
dt3 = sample(LETTERS,size = 100,replace = TRUE)
eBar(data.frame(x=dt3), x=~x)

dt4 = data.frame(x=sample(LETTERS,size = 200,replace = TRUE),
                 label = sample(c(0,1),size=200,replace=TRUE)
                 )
eBar(dt4, x=~x, y=NULL, series=~label)
```


## Add New Series
When add Series, Legend not update...

attr(yAxis) is optional.
```{r}
newSeries = list(data=rep(20,20)+rnorm(20),name = "new")
attr(newSeries, "yAxis") = list(min=15,max=25,type="value")
addSeries(k3, newSeries)
```


